Active Learning for SAT-Solver Benchmarking

### 2022-09-26 paper/paper.tex
Adapt title and authors
- remove (first) hyphen in title
- add further authors and re-format author block

\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage[labelfont=bf]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage[table]{xcolor}
\usepackage{tikz}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{pifont}
\usepackage{tablefootnote}
\usepackage{array}

@@

\title{Active-Learning for SAT-Solver Benchmarking}
\author{Tobias Fuchs}
\institute{Institute of Theoretical Informatics, \\ Karlsruhe Institute of Technology, Germany \\
\email{info@tobiasfuchs.de}}

@@

\section{Active-Learning for SAT-Solver Benchmarking}
\label{sec:main}
Our algorithm follows a simple three-step schema (Alg.~\ref{algALBenchmark}). After initializing the model $\mathcal{M}$, we incrementally \textit{select} a problem instance from the pool of instances, one at a time, evaluate the new solver $\hat{a}$ on it, and \textit{update} the model with the acquired result. We \textit{stop} when meeting some stopping condition.
Since the potential runtime of experiments is by magnitudes larger than the model's update time, we only consider incrementing our benchmark set by one instance at a time rather than using batches.
% For now, we also restrict ourselves to the aforementioned sequential one-instance-at-a-time process.
At the core of the model $\mathcal{M}$ is a prediction function $f\!: \left(\mathcal{A} \cup \left\lbrace \hat{a} \right\rbrace\right) \times \mathcal{I} \rightarrow \mathcal{V}$ that powers the decisions within the previously mentioned three steps.
Note that the prediction target values $\mathcal{V}$ are unspecified to allow for more flexibility within our particular approaches.
Refer to the next sections for more details.

>>>>

\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage[labelfont=bf]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage[table]{xcolor}
\usepackage{tikz}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{pifont}
\usepackage{tablefootnote}
\usepackage{array}
\usepackage[misc]{ifsym} % letter symbol to mark corresponding author

@@

\title{Active Learning for SAT-Solver Benchmarking}

\author{
	Tobias Fuchs (\Letter) \and
	Jakob Bach\orcidID{0000-0003-0301-2798} \and
	Markus Iser\orcidID{0000-0003-2904-232X}
}

\institute{
	Karlsruhe Institute of Technology (KIT), Karlsruhe, Germany \\
	\email{info@tobiasfuchs.de, jakob.bach@kit.edu, markus.iser@kit.edu}
}

\authorrunning{T. Fuchs et al.} % according to sample paper of template: first names are abbreviated; if there are more than two authors, 'et al.' is used.

@@

\section{Active Learning for SAT-Solver Benchmarking}
\label{sec:main}
Our algorithm follows a simple three-step schema (Alg.~\ref{algALBenchmark}). After initializing the model $\mathcal{M}$, we incrementally \textit{select} a problem instance from the pool of instances, one at a time, evaluate the new solver $\hat{a}$ on it, and \textit{update} the model with the acquired result. We \textit{stop} when meeting some stopping condition.
Since the potential runtime of experiments is by magnitudes larger than the model's update time, we only consider incrementing our benchmark set by one instance at a time rather than using batches.
% For now, we also restrict ourselves to the aforementioned sequential one-instance-at-a-time process.
At the core of the model $\mathcal{M}$ is a prediction function $f\!: \left(\mathcal{A} \cup \left\lbrace \hat{a} \right\rbrace\right) \times \mathcal{I} \rightarrow \mathcal{V}$ that powers the decisions within the previously mentioned three steps.
Note that the prediction target values $\mathcal{V}$ are unspecified to allow for more flexibility within our particular approaches.
Refer to the next sections for more details.
